Probability

### 2016-04-28 prob.tex
prob.tex "Classical Probability Spaces" Add the third example...

\makeatletter
\newtheoremstyle{indented}
  {3pt}% space before
  {3pt}% space after
  {\addtolength{\@totalleftmargin}{3.5em}
   \addtolength{\linewidth}{-3.5em}
   \parshape 1 3.5em \linewidth}% body font
  {}% indent
  {\bfseries}% header font
  {.}% punctuation
  {.5em}% after theorem header
  {}% header specification (empty for default)
\makeatother
\theoremstyle{indented}
%% \theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\pr}[2]{\langle #1, #2 \rangle}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ip}[2]{\langle #1 | #2 \rangle}
\newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\poss}{{\mbox{\wesa{possible}}}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}

@@

If we consider set with more values, the probability measure may give us more
information about the coins.

>>>>

\makeatletter
\newtheoremstyle{indented}
  {3pt}% space before
  {3pt}% space after
  {\addtolength{\@totalleftmargin}{3.5em}
   \addtolength{\linewidth}{-3.5em}
   \parshape 1 3.5em \linewidth}% body font
  {}% indent
  {\bfseries}% header font
  {.}% punctuation
  {.5em}% after theorem header
  {}% header specification (empty for default)
\makeatother
\theoremstyle{indented}
%% \theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\pr}[2]{\langle #1, #2 \rangle}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ip}[2]{\langle #1 | #2 \rangle}
\newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\poss}{{\mbox{\wesa{possible}}}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}

@@

If we consider set with more values, the probability measure may give
us more information about the coins. For example, despite $\imposs$
and $\poss$, we may also adopt three more values: $\unlikely$\ as
the interval~$\left(0,\frac{1}{2}\right]$, $\likely$\ as the interval~$\left(\frac{1}{2},1\right]$,
and $\overflow$\ as the empty set~$\emptyset$ which means the
total probability may be excessed than one. In particular, $\likely\vee\likely=\overflow$
because the probability of two disjoint events should not both bigger
than $\frac{1}{2}$. The complete rule for operator~$\vee$ on $\mathscr{L}_{5}=\left\{ \imposs,\poss,\unlikely,\likely,\overflow\right\} $
is defined in table~\ref{tab:The-operator-on}, or more abstractly,
we define $(a,b]\vee(c,d]=(a+c,b+d]\cap[0,1]$. The definition of
a probability measure can be modified as a function $\pmeas:\events\rightarrow\mathscr{L}_{5}$
such that: 
\begin{itemize}
\item $\pmeas(\Omega)\in\left\{ \poss,\likely\right\} $ or equivalently
$1\in\pmeas(\Omega)$, and 
\item for a collection $E_{i}$, of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\bigvee_{i}\pmeas(E_{i})$. 
\end{itemize}
\begin{table}
\center{%
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
$\vee$ & $\imposs$ & $\poss$ & $\unlikely$ & $\likely$ & $\overflow$\tabularnewline
\hline 
\hline 
$\imposs$ & $\imposs$ & $\poss$ & $\unlikely$ & $\likely$ & $\overflow$\tabularnewline
\hline 
$\poss$ & $\poss$ & $\poss$ & $\poss$ & $\likely$ & $\overflow$\tabularnewline
\hline 
$\unlikely$ & $\unlikely$ & $\poss$ & $\poss$ & $\likely$ & $\overflow$\tabularnewline
\hline 
$\likely$ & $\likely$ & $\likely$ & $\likely$ & $\overflow$ & $\overflow$\tabularnewline
\hline 
$\overflow$ & $\overflow$ & $\overflow$ & $\overflow$ & $\overflow$ & $\overflow$\tabularnewline
\hline 
\end{tabular}}

\caption{\label{tab:The-operator-on}The operator~$\vee$ on $\mathscr{L}_{5}=\left\{ \imposs,\poss,\unlikely,\likely,\overflow\right\} $}
\end{table}
\begin{example}{[}Two-coin probability space with $\mathscr{L}_{5}$-valued
probability measure{]} Under the new $\mathscr{L}_{5}$-valued requirement,
the probability measure in the first example becomes: 
\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) & = & \imposs\\
\pmeas(\{HH\}) & = & \unlikely\\
\pmeas(\{HT\}) & = & \imposs\\
\pmeas(\{TH\}) & = & \likely\\
\pmeas(\{TT\}) & = & \imposs\\
\pmeas(\{HH,HT\}) & = & \unlikely\\
\pmeas(\{HH,TH\}) & = & \likely\\
\pmeas(\{HH,TT\}) & = & \unlikely
\end{array} & \begin{array}{rcl}
\pmeas(\{HT,TH\}) & = & \likely\\
\pmeas(\{HT,TT\}) & = & \imposs\\
\pmeas(\{TH,TT\}) & = & \likely\\
\pmeas(\{HH,HT,TH\}) & = & \likely\\
\pmeas(\{HH,HT,TT\}) & = & \unlikely\\
\pmeas(\{HH,TH,TT\}) & = & \likely\\
\pmeas(\{HT,TH,TT\}) & = & \likely\\
\pmeas(\{HH,HT,TH,TT\}) & = & \likely
\end{array}\end{array}
\]
In this example, we can get the information that the first coin is
weighted and the second coin is double-headed. \qed\end{example}
